
\textbf{UC1 – Register User}

Allows a user to create a new account and become a RegisteredUser.

\textbf{UC2 – Authenticate User}

Allows a RegisteredUser to log in and access authenticated functionalities.

\textbf{UC3 – Access System as Unregistered User}

Allows a user to continue without authentication, with access limited to path querying and visualization.

\textbf{UC4 – Record Trip}

Allows a RegisteredUser to record a biking trip, including starting, pausing, resuming, discarding, and saving the trip, with real-time data displayed during recording.

\textbf{UC5 – View Trip History}

Allows a RegisteredUser to view previously recorded trips and access related statistics.

\textbf{UC6 – Enrich Trip with Weather Data}

Allows the system to retrieve and associate meteorological information with a completed trip, with optional manual refresh by the user.

\textbf{UC7 – Manually Insert Bike Path Information}

Allows a RegisteredUser to manually create and manage bike path information by specifying route details, path status, and obstacles.

\textbf{UC8 – Confirm Automatically Acquired Path Information}

Allows a RegisteredUser to review, confirm, correct, or discard bike path information automatically acquired during a trip before it becomes publishable.

\textbf{UC9 – Search Bike Paths}

Allows any User to search for bike paths between a specified origin and destination, retrieving candidate routes ranked by PathScore.

\textbf{UC10 – Visualize Bike Paths on Map}

Allows any User to visualize one or more bike paths on an interactive map based on search results.

 