\section{References}


\begin{thebibliography}{99}


    \bibitem{Specificationdocument}
    Software Engineering 2,
    \textit{2025/26 Requirement Engineering and Design Project Document}
    The specification for the 2025/26 Requirement Engineering and Design Project for the Software Engineering II course.

    \bibitem{RASDdocument}
    Software Engineering 2,
    \textit{Requirements Analysis and Specification Document}
    The RASD document for the 2025/26 Requirement Engineering and Design Project for the Software Engineering II course.

    \bibitem{academicslides}
    The slides on the WeBeep page of the Software Engineering II course.

    \bibitem{diagramsnet}
    JGraph,
    \textit{diagrams.net (draw.io)}, version 29.0.3.
    Available at: \url{https://www.diagrams.net/}.

    \bibitem{plantuml2025}
    Grasset, Arnaud.
    \textit{PlantUML - Open Source Unified Modeling Language (UML) Diagram Tool}.
    Available at: \url{https://plantuml.com/}

    % \bibitem{mermaid}
    % Mermaid Project,
    % \textit{Mermaid State Diagram Documentation}.
    % Available at: \url{https://docs.mermaidchart.com/}

    \bibitem{openweather}
    OpenWeather,
    \textit{OpenWeather API Documentation}.
    Available at: \url{https://openweathermap.org/api}

    \bibitem{openstreetmap}
    OpenStreetMap,
    \textit{OpenStreetMap API Documentation}.
    Available at: \url{https://wiki.openstreetmap.org/wiki/API}

    \bibitem{owasp-top10}
    OWASP Foundation - Standrd Awareness Document,
    \textit{OWASP Top 10 - 2021}.
    Available at: \url{https://owasp.org/Top10/2021/}

    \bibitem{OAuth2}
    D. Hardt, \textit{The OAuth 2.0 Authorization Framework}, datatracker.ietf.org, Oct. 2012.
    Available at: \url{https://datatracker.ietf.org/doc/html/rfc6749}

    \bibitem{rest-tutorial}
    REST API Tutorial,
    \textit{REST API Tutorial: Learn REST API Design},
    Available at: \url{https://www.restapitutorial.com}.

    \bibitem{postgresql2025}
    The PostgreSQL Global Development Group.
    \textit{PostgreSQL 15 Documentation}.
    Available at: \url{https://www.postgresql.org/docs/15/}

    \bibitem{postgis2025}
    PostGIS Project.
    \textit{PostGIS 3.3 Documentation - Spatial Database Extender for PostgreSQL}.
    Available at: \url{https://postgis.net/documentation/}

    \bibitem{figma2025}
    Figma, Inc.
    \textit{Figma - Collaborative Design Platform}.
    Available at: \url{https://www.figma.com/}

    \bibitem{gdpr}
    European Union, \textit{General Data Protection Regulation (GDPR)}, Official Journal of the European Union, 2016/679.
    Available at: \url{https://gdpr-info.eu/}.

\end{thebibliography}
